---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# crrf

<!-- badges: start -->
<!-- badges: end -->

The goal of crrf is to enable fitting of the Firth-penalized Fine-Gray model for competing risks regression. The Firth penalty allows for parameter estimation in the case of monotone likelihood. This work was inspired by a SAS macro by Kohl et al., 2016 (https://doi.org/10.1016/j.cmpb.2014.11.009).

## Installation

You can install the development version of crrf from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("annaSeffernick/crrf")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(crrf)
# Generate Data
set.seed(12345)
n=100
tm=rexp(n)
ev=factor(rbinom(n,2,0.3))

x=rnorm(n)
y=rbinom(n,1,0.5)
u=runif(n)

dset=cbind.data.frame(tm=tm,ev=ev,x=x,y=y,u=u)
# fit the model
crrf.fit=crrf(Surv(tm,ev)~x+y+u,etype="1",dset,firth=TRUE,CI=TRUE)
crrf.fit$CI.tbl
```

